When are Fuzzy Extractors Possible?

### 2014-10-04 info-bounds/FuzzyExtPossibility.tex
working through body of paper

Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

@@

\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.  We begin with distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.   Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.  We use universal hashing to disambiguate points.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.  We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.  We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.  For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

 The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.  The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.  Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.

Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

\bnote{are these really affine lines?}
\bnote{I'm writing these, very rough draft}

@@

Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

@@

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
%\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  We cover the distribution-aware setting in \secref{sec:distribution aware}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\noindent \textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

In an ideal world, we could provide a reproduce functionality as an oracle.  In this world, the key is learned if a close point is provided, and no other information is leaked.  In the rest of this work, we compare security to this ideal world.  We call this fuzzy min-entropy:

\begin{definition}
\label{def:fuzzy min-ent}
A distribution $W$ in a metric space $(\mathcal{M}, \dis)$ has $(t, k)$-fuzzy min-entropy, denoted $\Hfuzz(W) \ge k$ if the following holds:
\[
\forall m\in \mathcal{M},  \sum_{w\in W | \dis(w, m)\le t} \Pr[W=w] \leq 2^{-k}.
\]
\end{definition}

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}

The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
\lemref{lem:fuzz necessary} still applies.  
This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.

There are many distributions with fuzzy min-entropy for which no in the fuzzy extractor is known to be secure.  There are also no known impossibility results for distributions with fuzzy min-entropy.  Thus, the situation for fuzzy extractors is quite unclear.
As a reminder, our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.  We begin with the simpler distribution-aware setting and then consider the complicated distribution-oblivious setting.

\subsection{Distribution-aware setting}
\label{sec:distribution aware}
To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  We call this type of algorithm \emph{distribution-aware}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.  It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.

\section{Distribution-Aware Information-Reconciliation}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.

@@

Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

@@

\subsection{Secure sketches for all distributions with fuzzy min-entropy}
The hashing approach just described does not work for arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.

Dealing with non-flat distributions requires a new strategy. % The fuzzy extractor must be aware of the density of the current ball.  
Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

@@

\textbf{Note:} In all of the previous results, we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Going forward we will consider specific metric spaces, namely the Hamming metric.
\section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
\label{sec:dist oblivious}

>>>>

Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in \propref{prop:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

@@

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

In the fuzzy extractor case, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$ (preimages of each $\key$ under $\rep(\cdot, p)$).  For each of these regions, the adversary knows that possible $w$ lie $t$-far from the boundary of the region.  However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).  This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.

The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.  The result for fuzzy extractors is more delicate.  It requires the fuzzy extractor to correct $t = \omega(n^{1/2}\log n)$ errors~(where $n$ is the length of the string) and have perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
This result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

@@

Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

@@

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
%\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

@@

In this section, we define fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with modifications.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
%This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  
We discuss distribution-aware algorithms in \secref{sec:distribution aware def}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

\noindent In the above definitions, the errors are chosen before $ss$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$),  there is no correctness guarantee.  
A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:

\begin{definition}
Let $\mathcal{M}$, $\chi$ be finite sets.
A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

In an ideal world, we could provide a reproduce functionality as an oracle.  In this world, the key is output if a close point is provided, and no response is provided otherwise.  We call the performance of an adversary in this ideal world fuzzy min-entropy:

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}

Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):%If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal:
%For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{proposition}
\label{prop:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result)
Our goal is to provide a super-logarithmic length key when provided with super-logarithmic fuzzy min-entropy.  We now describe distribution-aware algorithms.

\subsection{Distribution-aware algorithms}
\label{sec:distribution aware def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
We call an algorithm with complete information on the distribution $W$ \emph{distribution-aware}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w,w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume distribution-aware algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) distribution-aware constructions of sketches and extractors is an interesting problem.

\section{Sufficiency of $\Hfuzz$ for Distribution-Aware Algorithms}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.

@@

Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  That is, 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

@@

\subsection{Secure sketches for all distributions with $\Hfuzz$}
The hashing approach just described does not work for arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.

Dealing with non-flat distributions requires a new strategy. % The fuzzy extractor must be aware of the density of the current ball.  
Many solutions for manipulating high entropy distributions leverage a solution for flat distributions and use the fact that high entropy distributions are convex combinations of flat distributions.  However, a distribution with high fuzzy min-entropy may be formed from component distributions with little or no fuzzy min-entropy.  It is unclear how to leverage the convex combination property in this setting.  \bnote{I took out the discussion of the appendix, don't know if it helps}%In \apref{sec:convex comb}, we show that it is difficult to exploit this property in our scenario.  The issue is that a distribution with high fuzzy min-entropy may be formed from component distributions each of which have no fuzzy min-entropy.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of $\Hfuzz$ for Distribution-Oblivious Secure Sketches}
\label{sec:dist oblivious}
